---
title: 'MockDataGen R Markdown / Module #12'
author: "Ronald Garcia"
date: "2025-04-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Function 1: generate_names()

Purpose: 
Generates a list of randomly selected full names

Inputs: 
input integer (n) for number of names to generate, must be a positive whole number. 

Outputs:
A character vector of the length inputed (n). 

Additional Info: 
The function will randomly pair first and last names from each of the two vectors. Names may possibly repeat if n is larger than number of unique combinations. 

```{r cars}
#Example
generate_names <- function(n = 10) {
  first_names <- c("John", "Emily", "Alex", "Sam", "Chris", "Jordan")
  last_names <- c("Smith", "Johnson", "Garcia", "Lee", "Patel", "Davis")
  sample(paste(sample(first_names, n, replace = TRUE),
               sample(last_names, n, replace = TRUE)), n)
}

generate_names(5)

```

Function 2: generate_emails()

Purpose: Generate a list of randomly selected emails

Inputs: 
(n) number of emails needed.

Outputs:
character vector with (n) number of emails needed in correct formats.

Additional Info: 
This will use full lowercase formatiing. The emails are created using the names in the "names" variable.

```{r}
#Example
generate_emails <- function(n = 10) {
  names <- tolower(gsub(" ", ".", generate_names(n)))
  domains <- c("example.com", "testmail.org", "mockdata.io")
  paste0(names, "@", sample(domains, n, replace = TRUE))
}

generate_emails(5)

```

Function 3: generate_ages()

Purpose: Generates random ages if needed for data 

Inputs:
(n) number of ages needed. min_age = minimum age allowed. max_age = maximum age allowed. 

Outputs:
Vector with the ages.

Additional Info:
Ages are repeatable. 
```{r}
#Example
generate_ages <- function(n = 10, min_age = 18, max_age = 30) {
  sample(min_age:max_age, n, replace = TRUE)
}


generate_ages(5)


```

Function 4: generate_addresses()

Purpose: Generates random  addresses if needed for data.

Inputs:
(n) number of addresses needed.

Outputs:
Vector with all the addresses needed.

Additional Info:
It combines random street numbers, names, cities, states, and zip codes.
```{r}
#Example
generate_addresses <- function(n = 10) {
  streets <- c("Maple St", "Oak Ave", "Pine Rd", "Elm Dr", "Cedar Ln", "Birch Blvd")
  cities <- c("Springfield", "Rivertown", "Hillview", "Lakewood", "Greenville")
  states <- c("CA", "NY", "TX", "FL", "IL")
  zips <- sample(10000:99999, n, replace = TRUE)
  
  addresses <- paste0(
    sample(100:9999, n, replace = TRUE), " ",
    sample(streets, n, replace = TRUE), ", ",
    sample(cities, n, replace = TRUE), ", ",
    sample(states, n, replace = TRUE), " ",
    zips
  )
  
  return(addresses)
}

generate_addresses(5)
```

